Rust for Scientific Computing

### 2025-08-30 paper/main.tex
move paper to own subfolder

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/stackoverflow-popular-languages.pdf}%
    \includegraphics[width=0.5\textwidth]{figures/pypi-org-used-languages.pdf}
    \includegraphics[width=0.5\textwidth]{figures/stackoverflow-loved-language.pdf}%
    \includegraphics[width=0.5\textwidth]{figures/stackoverflow-desired-language.pdf}
    \caption{TODO}
\end{figure}

@@

\subsection{Foundational Components}
\subsubsection{Linear Algebra \& Arrays}
(nalgebra, ndarray) (dense, sparse matrices, solvers)

@@

\subsection{Computational Methods}
\subsubsection{Optimization}
\subsubsection{Differential Equations}
(ODEs, PDEs)

@@

\subsection{High-Performance \& Scalable Computing}
\subsubsection{Parallel Computing}
(rayon, compare to openmp, MPI bindings)

@@

\subsection{Creature Comforts}
\subsubsection{Debugging}
(Rust Errors as values, tracing, logging) ecosystem

@@

\subsection{Visualization}
\subsubsection{Plotting (2D)}
plotters, plotlib, gnuplot bindings

@@

Meshing (honeycomb)

@@

@@

qoqo\\
A toolkit to represent quantum circuits by HQS Quantum Simulations.

@@

qhull-rs\\
Qhull computes the convex hull, Delaunay triangulation, Voronoi diagram, halfspace
intersection about a point, furthest-site Delaunay triangulation, and furthest-site Voronoi
diagram.

@@

Roqoqo\\
A quantum computing toolkit in Rust.

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/stackoverflow-popular-languages.pdf}%
    \includegraphics[width=0.5\textwidth]{figures/pypi-org-used-languages.pdf}
    \caption{
        Usage of programming languages according to (A) stackoverflow.com and (B) pypi.org.
    }
\end{figure*}
\begin{figure*}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/stackoverflow-loved-language.pdf}%
    \includegraphics[width=0.5\textwidth]{figures/stackoverflow-desired-language.pdf}
    \caption{
        Popularity of the Rust programming language.
    }
\end{figure*}
\begin{figure*}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/crates-io-release-numbers.pdf}
    \caption{
        Number of releases of all included crates.
        Measure of overall growth of the field.
    }
\end{figure*}

@@

\subsection{Foundational Components}
Definition:\\
Lowest level of library considered in this review. Other crates depend on these
foundational crates.

\subsubsection{Linear Algebra \& Arrays}
(nalgebra, ndarray) (dense, sparse matrices, solvers)

@@

\subsection{Computational Methods}
Definition:\\
They are typically built on top of Foundational Components. Can also generalize over
many of these (such as different linear algebra crates).

\subsubsection{Optimization}
\subsubsection{Differential Equations}
(ODEs, PDEs)

@@

\subsection{High-Performance \& Scalable Computing}
Definition:\\
Frameworks/libraries that allow greater scalability or usage of additional resources
such as GPUs/TPUs etc.

\subsubsection{Parallel Computing}
(rayon, compare to openmp, MPI bindings)

@@

\subsection{Creature Comforts}
Definition:\\
Everything that is still missing

\subsubsection{Debugging}
(Rust Errors as values, tracing, logging) ecosystem

@@

\subsection{Visualization}
Definition:\\
Libraries which can be used to visualize results. (self-explanatory)

\subsubsection{Plotting (2D)}
plotters, plotlib, gnuplot bindings

@@

Meshing (honeycomb) (maybe this should be in section "Computational Methods" / "Differential
Equations")

@@

\begin{itemize}
    \item Job Opportunities remain a problem in Rust
\end{itemize}

@@

qoqo (Roqoqo)\\
A toolkit to represent quantum circuits by HQS Quantum Simulations.

@@

qhull-rs\\
Safe Rust Qhull bindings. Qhull computes the convex hull, Delaunay triangulation,
Voronoi diagram, halfspace intersection about a point, furthest-site Delaunay triangulation, and
furthest-site Voronoi diagram.

@@
